\clearpage{\pagestyle{empty}\cleardoublepage}
\begin{thebibliography}{3}
\addcontentsline{toc}{chapter}{Bibliografia}

\bibitem{gse2010} Gestore Servizi Energetici (GSE) \
  - Direzione Studi, Statistiche e Servizi Specialistici, \
  \emph{Rapporto Statistico 2010 -- Solare Fotovoltaico}, 4/2011 \\
  \url{www.ording.roma.it/archivio/9716-gse_rapporto_statistico_2010.pdf}

\bibitem{photon2010} C. Podewils (2010), \
  \emph{Monitoraggi Immaturi}, \
  Photon - il mensile del fotovoltaico, 8/2010, \
  pagg. 22--24.

\bibitem{castaner02} L. Castaner, S. Silvestre (2002), \
  \emph{Modelling Photovoltaic Systems using PSpice}, \
  ed. John Wiley \& Sons, Chichester, UK.

\bibitem{bellini09} A. Bellini, S. Bifaretti, V. Iacovone, C. Cornaro (2009), \
  \emph{Simplified model of a photovoltaic module}, \
  Applied Electronics.

\bibitem{patel08} H. Patel, V. Agarwal (2008), \
  \emph{MATLAB-based modeling to study the effects of partial shading 
  on PV array characteristics}, \
  IEEE Transactions on Instrumentation and Measurement, vol. 58, no. 5,
  pp. 302-310.

\bibitem{roman06} E. Roman et al. (2006), \
  \emph{Intelligent PV module for grid-connected PV systems},
  IEEE Transactions on Industrial Electronics, vol. 53, no. 4,
  pp. 1066-1073.

\bibitem{sung09} H. sung Kim et al. (2009) \
  \emph{A highly efficient PV system using a series connection of DC-DC 
  converter output with a photovoltaic panel}, \
  Renewable Energy, Volume 34, Issue 11, 
  pp. 2432-2436.

\bibitem{scambioposto} Gestore Servizi Energetici (GSE) \
  \emph{Scambio sul posto per le fonti rinnovabili}, \\
  \url{http://www.gse.it/ATTIVITA/SSP/Pagine/default.aspx}

\bibitem{testconditions} FSEC Standard 202-10, 
   \emph{Test Method for Photovoltaic Module Power Rating}, \\
   \url{http://www.fsec.ucf.edu/en/publications/pdf/standards/FSECstd_201-10.pdf}

\bibitem{criteriallacciamento} Enel Spa (2007)\
   - Divisione Infrastrutture e reti, \             
   \emph{Criteri di allacciamento di impianti di produzione alla
   rete BT di Enel Distribuzione}, ed. 2.2, \\
   \url{http://www.enel.it/it-IT/doc/reti/enel_distribuzione/produttori/Guida_per_le_connessioni_ed_2_1_Gennaio_2011.pdf}

\bibitem{dirks06} E. Dirks, A.M. Gole, T.S. Molinski (2006), 
  \emph{Performance evaluation of a building integrated photovoltaic array using an Internet based monitoring system}, \
  Power Engineering Society General Meeting, 2006.

\bibitem{kolodenny08} W. Kolodenny, M. Prorok, T. Zdanowicz, N. Pearsall, R. Gottschalg (2008), \
  \emph{Applying modern informatics technologies to monitoring photovoltaic (PV) modules and systems}, \
  Photovoltaic Specialists Conference 2008 11-16 May 2008, \
  pp.1-5.

\bibitem{kolodenny06} W. Kolodenny (2006), \
  \emph{Efficient Data Analysis with Modern Analytical System Developed for Use in Photovoltaic (PV) Monitoring System}, \
  Photonics and Microsystems, International Students and Young Scientists Workshop, June 30 2006-July 2 2006 \
  pp.26-29.

\bibitem{xiaoli11} X. Xiaoli, Q. Daoe (2011), 
  \emph{Remote monitoring and control of photovoltaic system using wireless sensor network} \
  International Conference on Electric Information and Control Engineering (ICEICE) 15-17 April 2011, \
  pp.633-638. 

\bibitem{aristizabal06} A.J. Aristizabal, C.A. Arredondo, J. Hernandez, G. Gordillo (2006), \
  \emph{Development of Equipment for Monitoring PV Power Plants, using Virtual Instrumentation}, \
  Conference Record of the 2006 IEEE 4th World Conference on Photovoltaic Energy Conversion, vol.2, \
  pp.2367-2370.

\bibitem{guozhen09} H. Guozhen, C. Tao, C. Changsong, D. Shanxu (2009), \
  \emph{Solutions for SCADA system communication reliability in photovoltaic power plants}, \
  IEEE 6th International Power Electronics and Motion Control Conference, 17-20 May 2009, \
  pp.2482-2485. 

\bibitem{zigbee} The ZigBee Alliance \
  \url{http://www.zigbee.org}

\bibitem{dirisa10} Socomec - Interrutori industriali e Sistemi di Continuit\`a, \
  \emph{Presentazione Diris A10}, \
  \url{http://www.socomec.com/presentazione-dirisa10_it.html}

%% \bibitem{benghanem98} M. Benghanem, A Maafi (1998), \
%%   \emph{Data acquisition system for photovoltaic systems performance monitoring}, \
%%   IEEE Transactions on Instrumentation and Measurement, \
%%   vol.47, no.1, pp.30-33.

\bibitem{camera2003} Camera dei Deputati, \
  \emph{Decreto Legislativo 29 dicembre 2003, n. 387}, \
  \url{http://www.camera.it/parlam/leggi/deleghe/testi/03387dl.htm}
   
\bibitem{erlapplication} \emph{Erlang Application}, \\
   \url{http://www.erlang.org/doc/man/application.html}

%% \bibitem{erlang} Erlang, \emph{"Open Source Erlang"} \newline http://www.erlang.org/


%% \bibitem{santoroframe} C. Santoro (2007), \emph{"An Erlang Framework for Autonomous Mobile Robots"}, ACM Erlang Workshop 2007, Freiburg, Germany.

%% \bibitem{siegwart} R. Siegwart, I.R. Nourbakhsh (2004), \emph{Autonomous Mobile Robots}, MIT Press.

%% \bibitem{appinknowledge} Appin Knowledge Solutions (2007), \emph{Robotics}, Infinity Science Press.

%% \bibitem{cohenkoss92} C. Cohen, F. V. Koss (1992), \emph{A Comprehensive Study of Three Object Triangulation}, Mobile Robots VII, SPIE Vol. 1831,1992.

%% \bibitem{beomcho}  Beom H. R., CHO H. S. (1995), \emph{Mobile robot localization using a single rotating sonar and two passive cylindrical beacons}, Robotica vol. 13 (3), pp. 243-252 (15 ref.), Cambridge University Press, 1995.

%% \bibitem{carvalho03} J. S. Esteves, A. Carvalho, C. Couto (2003), \emph{Generalized Geometric Triangulation Algorithm for Mobile Robot Absolute Self-Localization}, International Symposium on Industrial Electronics, Rio de Janeiro, Brazil, June 9-12, 2003.

%% \bibitem {carvalho06} J. S. Esteves, A. Carvalho, C. Couto (2006), \emph{ An improved
%% version of the Generalized Geometric Triangulation algorithm}, II European-Latin-American Workshop on Engineering
%% Systems, Faculdade de Engenharia da Universidade do Porto, Porto, Portugal, June 21-23, 2006.

%% \bibitem {carvalho062} J. S. Esteves, A. Carvalho, C. Couto (2006), \emph{  Position and Orientation Errors in Mobile Robot, Absolute Self-Localization Using an Improved Version of the Generalized Geometric Triangulation Algorithm}, International Conference on Industrial Technology, Mumbai, India, 2006, p. 830-835.

%% \bibitem{whereami} J. Borenstein, H. R. Everett, L. Feng (1996), \emph{"Where am i? Systems and Methods for Mobile Robot Positioning"} \newline http://www-personal.umich.edu/~johannb/shared/pos96rep.pdf 

%% \bibitem{homepage} Eurobot 2008 - DIIT TEAM, \emph{"Eurobot 2008 - DIIT TEAM"} \newline http://eurobot.diit.unict.it/

%% \bibitem{eurobothome} Eurobot Open, \emph{"Eurobot"} \newline http://www.eurobot.org/

%% \bibitem{eurobot2008home} Eurobot 2008, \emph{"Eurobot 2008: Home"}\newline http://eurobot.fh-heidelberg.de/

%% \bibitem{regoleeurobot} Eurobot Open 2008, Mission to Mars \emph{"Rules 2008 - Revision 1"} \newline http://www.eurobot.org/eng/docs/2008/E2008\_Rules-EN-v2.pdf 

%% \bibitem{sitodiit} Eurobot 2008 - DIIT TEAM, \emph{"Docs"} \newline http://eurobot.diit.unict.it/topic-docs.php

%% \bibitem{e3zlr81} Omron Corporation, \emph{"E3Z-LT/LR/LL Data Sheet"} \newline http://www.ia.omron.com/data\_pdf/data\_sheet/e3z-lt\_-lr\_-ll\_dsheet\_csm437.pdf

%% \bibitem{18f2431} Microchip Technology Inc., \emph{"PIC18F2331/2431/4331/4431 Data Sheet"} \newline http://ww1.microchip.com/downloads/en/DeviceDoc/39616C.pdf

%% \bibitem{l293d} STMicroelectronics , \emph{" L293D-L293DD PUSH-PULL FOUR CHANNEL DRIVER WITH DIODES"} \newline http://www.st.com/stonline/products/literature/ds/1330.pdf

%% \bibitem{python} Python Software Foundation , \emph{"Python Programming Language - Official Website"} \newline http://www.python.org/

%% \bibitem{erlang} Erlang, \emph{"Open Source Erlang"} \newline http://www.erlang.org/

%% \bibitem{wikinewton} Wikipedia, \emph{Newton's Method} \newline http://en.wikipedia.org/wiki/Newton\_method

%% \bibitem{wikii2c} Wikipedia, \emph{"I2C"} \newline http://it.wikipedia.org/wiki/I\%C2\%B2C

%% \bibitem{wikilimitecentrale} Wikipedia, \emph{"Teorema del Limite Centrale"} \newline http://it.wikipedia.org/wiki/Teorema\_del\_Limite\_Centrale

%% \bibitem{wikifsm} Wikipedia, \emph{"Finite State Machine"} \newline http://en.wikipedia.org/wiki/Finite\_state\_machine

\end{thebibliography} 
